---
title: "Now it's time to use customed fonts!!! "
author: "耿远昊"
date: "March 2020"
output:
  pdf_document:
    latex_engine: lualatex
  word_document: default
header-includes:
  - \usepackage{amsmath}
  - \usepackage{ctex}
  - \usepackage{fontspec}
  - \setmainfont{SegoePrint}
  - \everymath{\displaystyle} 
  - \usepackage{booktabs}
  - \usepackage{algorithm}
  - \usepackage{algorithmic}
  - \usepackage{color}
  - \usepackage{graphicx}
  - \usepackage{amssymb}
  - \usepackage{amsfonts}
  - \DeclareMathOperator*{\argmax}{argmax}
  - \DeclareMathOperator*{\argmin}{argmin}
  - \renewcommand{\algorithmicrequire}{ \textbf{Input:}}
  - \renewcommand{\algorithmicensure}{ \textbf{Output:}}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Formula:

First, we will test on \LaTeX: $\Sigma_{k=1}^{n}k^{2}$,  $\iint_{\mathbb{R}^2}\frac{x}{y}d\omega$. It seems perfect!

$$\sum_{n=1}^{\infty} 2^{-n} = 1$$

# Plots:

Then, let us check several key points:
\newline
(a) r-base plot
```{r, fig.showtext=TRUE, message=FALSE,fig.height = 2.5, fig.width = 4.8,fig.align = "center"}
library(showtext)
showtext_auto(enable = TRUE)
font_add('SegoePrint', 'SegoePrint.ttf')
plot(pressure,xlab='You can change the fonlubridatet now!',family='SegoePrint',tck=-0.05
                                                         ,main='r-base plot'
                                                         ,cex=0.6,cex.main=1
                                                         ,cex.lab=0.9,cex.axis=0.7)
```
(b) ggplot2

```{r, fig.showtext=TRUE, message=FALSE,fig.height = 3.3, fig.width = 4,fig.align = "center"}
library(ggplot2)
library(quantmod)
data("economics", package = "ggplot2")
economics$returns_perc <- c(0, diff(economics$psavert)/
economics$psavert[-length(economics$psavert)])
brks <- economics$date[seq(1, length(economics$date), 12)]
lbls <- lubridate::year(economics$date[seq(1,
length(economics$date), 12)])
ggplot(economics[1:100, ], aes(date, returns_perc)) +
    geom_area() +
    scale_x_date(breaks=brks, labels=lbls) +
    theme(axis.text.x = element_text(angle=90)) +
    labs(title="Area Chart",
    y="Returns for Personal savings",
    caption="Source: economics")+
    theme(plot.title = element_text(hjust = 0.5))+
    theme(text=element_text(family="SegoePrint",size=9))
```
(c) r-base plot with chinese
```{r, fig.showtext=TRUE, message=FALSE,fig.height = 2.8, fig.width = 4.8,fig.align = "center"}
font_add('Seafood', 'Seafood.ttf')
plot(pressure,xlab='现在可以更改字体了！',family='Seafood',tck=-0.05
                                                         ,main='基础包作图'
                                                         ,cex=0.6,cex.main=1.3
                                                         ,cex.lab=1.2,cex.axis=1.05)
```

(d) ggplot2 with chinese

```{r, fig.showtext=TRUE, message=FALSE,fig.height = 3.8, fig.width = 4,fig.align = "center"}
library(ggplot2)
library(quantmod)
ggplot(economics[1:100, ], aes(date, returns_perc)) +
    geom_area() +
    scale_x_date(breaks=brks, labels=lbls) +
    theme(axis.text.x = element_text(angle=90)) +
    labs(title="分区图",
    y="个人储蓄的回报",
    caption="来源： Economics")+
    theme(plot.title = element_text(hjust = 0.5))+
    theme(text=element_text(family="Seafood",size=13))
```

## Table:

\begin{center}
\begin{tabular}{ccc}
	\toprule
	First name & Last name & Grade \\
	\midrule
	John & B & 7.5 \\
	Bob & A & 5.2 \\
	Tom & E & 6.4 \\
	Gary & D & 2.3 \\
	Richard & A & 2\\
	Bach & C & 0.6\\
	\midrule
	6 Person & A & 7.5\\
	\bottomrule
\end{tabular}
\end{center}

## Algorithm

\begin{algorithm}
	\caption{AdaBoost二分类问题}
	\begin{algorithmic}[1]
		\REQUIRE{$M$个弱二分类器，$N$个训练样本，迭代轮数$T$}
		\ENSURE{$H_{Boost}$}
		\STATE $\alpha_0 \gets 0$
		\STATE $h_0(x_i) \gets 0,i=1,...,N$
		\FOR{each $t \in [1,T]$}
		\STATE $H_{t-1} \gets \sum_{i=0}^{t-1}\alpha_i h_0(x_i)$
		\STATE $w_{t,i} \gets e^{-y_i H_{t-1}(x_i)}$
		\STATE $h_t\gets\mathop{\argmin_{h}\sum_{i=1}^{N}w_{t,i} \mathbb{I}(y_i=h(x_i))}$
		\STATE $W_{t,i}\gets \frac{w_{t,i}}{\sum_{i=1}^N w_{t,i}}$
		\STATE $e_t\gets\sum_{i=1}^N W_{t,i}\mathbb{I}(y_i\ne h_t(x_i))$
		\IF{$e_t>\frac{1}{2}$}
		\STATE Break
		\ELSE
		\STATE $\alpha_t\gets\frac{1}{2}\ln\frac{1-e_t}{e_t}$
		\ENDIF
		\ENDFOR
		\RETURN $H_{Boost}=sign(\sum_{i=1}^T\alpha_i h_i(x))$
	\end{algorithmic}
\end{algorithm}

## How to do it?

(1) You should find your system font folder.
(2) Download the *.ttf file which represent your customed font.
(3) Copy the file into your font folder.
(4) Download `showtext` package.
(5) Use `showtext_auto(enable = TRUE)` and `font_add('*', '*SegoePrint.ttf*.ttf')` to register your font.
(6) Change the font family setting in your code.
(7) Change the chunk head with `fig.showtext=TRUE`, or it won't work!
(8) Add head setting in your Rmd file. In this example, it was wirtten like this:
\begin{figure}[htp]
	\centering
	\includegraphics[height=100mm,width=100mm]{font.png}
	\caption{Rmd Head of This Example}
	\label{leaves}
\end{figure}

If you have the same problem with matplotlib in python, you can look this [\textcolor{red}{instruction}](https://github.com/GYHHAHA/God-pit) about how to configurate default custom fonts in matplotlib. At least, it works for me after looking into a large number of referances (which some of them make me painful and confused).

Hope this guide can help you!